---
title: 'How Does Stigma Affect People With Chronic Pain?: Univariate Analysis'
author: "Usman Rashid"
date: "02/07/2021"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

```{r data_setup, echo=FALSE, include=FALSE}

# Packages Used:
require(ggplot2)
require(lme4)
require(car)
require(MASS)
require(sjstats)
require(fBasics)
require(ggpubr)
require(reshape2)
require(phia)
require(emmeans)
require(multcomp)
require(jtools)
require(rsq)
require(r2glmm)
require(sjPlot)
require(MuMIn)
require(effects)
require(optimx)
require(margins)
require(cAIC4)
require(ggsignif)
require(forcats)
require(gdata)
require(splines)
require(dplyr)
require(ggsci)
require(blmeco)
require(lemon)
require(ggExtra)

knit_print.data.frame <- lemon_print
options(knitr.kable.NA = '')

source('Stats-Helpers.R')

# Load data
Datasource <- read.csv("DataTable.csv")
Datasource$PartID <- as.factor(Datasource$PartID)

Datasource$Gender <- make.factor(Datasource$Gender, levels = seq(1, 3), labels = c("Male", "Female", "Other"))

Datasource$Ethnicity <- make.factor(Datasource$Ethnicity, levels = seq(1, 4), labels = c("European", "MÄori", "Pacific", "Asian"))

Datasource$Relationship <- make.factor(Datasource$Relationship, levels = seq(1, 6), labels = c("Single", "In a relation", "Married/De facto", "Civil union", "Divorced/sep.", "Widowed"))

Datasource$Employment <- make.factor(Datasource$Employment, levels = seq(1, 6), labels = c("Employed", "Unemployed/benefit", "Work at home", "Retired", "Student", "Other"))

Datasource$Diagnosis <- make.factor(Datasource$Diagnosis, levels = seq(1, 14), labels = c("Fibromyaliga", "CRPS", "Spinal pathology", "Headache/migraine", "Endometriosis", "Osteoarthritis", "Inflam/Rhe. art.", "Multiple diagnoses", "Label Missing", "Other/unknown", "Sensitization", "Mesh", "Neuropathy", "Injury"))

Datasource$Pain.loc <- make.factor(Datasource$Pain.loc, levels = seq(1, 8), labels = c("Head/face", "Neck/back", "Upper limb", "Chest", "Abdomen/pelvis", "Hips/buttocks", "Lower limb", "Other/widepread"))

Datasource$Mental.health <- make.factor(Datasource$Mental.health, levels = seq(0, 1), labels = c("Diagnosis", "No diagnosis"))

Datasource$Daily.opioid.intake <- Datasource$Daily.opioid.intake ^ (1/4)
Datasource$Use.opioids <- make.factor(as.numeric(Datasource$Daily.opioid.intake > 0), levels = c(0, 1), labels = c("No", "Yes"))

Datasource$Pain.duration <- Datasource$Pain.duration ^ (1/4)
```

\newpage

# Univariate Illustrations and Statistics

## Summary

```{r summary, echo=FALSE, include=TRUE, warning=F, render=lemon_print}
head(Univariate.summary.table(Datasource, exclude.vars = c("PartID"), na.rm = T), n = 100L)
```

\newpage

## Age

```{r age, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Age", na.rm = T)
Data$graph
```

```{r age_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Gender

```{r gender, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Gender")
Data$graph
```

```{r gender_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Ethnicity

```{r ethn, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Ethnicity")
Data$graph
```

```{r ethn_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Relationship

```{r relshp, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Relationship")
Data$graph
```

```{r relshp_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Employment

```{r emply, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Employment")
Data$graph + coord_flip()
```

```{r emply_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Diagnosis

```{r diag, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Diagnosis")
Data$graph + coord_flip()
```

```{r diag_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Organic Beliefs

```{r org_bel, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Beliefs.organic", na.rm = T)
Data$graph
```

```{r org_bel_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Psychological Beliefs

```{r psy_bel, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Beliefs.psych", na.rm = T)
Data$graph
```

```{r psy_bel_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Pain Duration

```{r pain_dur, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Pain.duration", na.rm = T)
Data$graph
```

```{r pain_dur_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Pain Location

```{r pain_loc, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Pain.loc")
Data$graph + coord_flip()
```

```{r pain_loc_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Use Opioids

```{r use_op, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Use.opioids")
Data$graph + coord_flip()
```

```{r use_op_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Daily Opioid Intake

```{r opi, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Daily.opioid.intake", na.rm = T)
Data$graph
```

```{r opi_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Mental Health

```{r men_hel, echo=FALSE, include=TRUE, warning=F}
Data <- present.factor(Datasource, "Mental.health")
Data$graph
```

```{r men_hel_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Stigma

```{r stigma, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Stigma.total", na.rm = T)
Data$graph
```

```{r stigma_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Pain Intensity

```{r pain_int, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Pain.intensity", na.rm = T)
Data$graph
```

```{r pain_int_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Disability

```{r disa, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Disability", na.rm = T)
Data$graph
```

```{r disa_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Depression

```{r depr, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Depression.phq9", na.rm = T)
Data$graph
```

```{r depr_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```

\newpage

## Support

```{r supr, echo=FALSE, include=TRUE, warning=F}
Data <- present.continuous(Datasource, "Support.oss3", na.rm = T)
Data$graph
```

```{r supr_table, echo=FALSE, include=TRUE, render=lemon_print}
head(Data$table, n = 100L)
```